18 month progress report

### 2017-03-24 reports/progress_1/progress_1.tex
In progress report, subfigure Z statistics.

A sample of $Z$ statistics are shown in Figure \ref{fig:p_values} and significant pixels are shown in Figure \ref{fig:critical_values}. The Bonferroni correction was used to correct for multiple testing. The $Z$ statistics within image varied scan to scan, suggesting images in the test set were not quite as similar to each other as hoped for. Common significant pixels were picked up by the statistic, especially on the left edge. Fortunately only a few significant pixels were picked up from the 3D printed sample, implying only a few false positives were detected.

\begin{figure}
	\centering
	\centerline{
	\includegraphics[width = 0.5\textwidth]{../figures/meanVar/p_values.png}
	}
	\caption{A sample of $Z$ statistics obtained from comparing a scan from the test set to the true image. The $Z$ statistics were transformed using the standard Normal c.d.f.}
	\label{fig:p_values}
\end{figure}

\begin{figure}
	\centering
	\centerline{
	\includegraphics[width = 0.5\textwidth]{../figures/meanVar/critical_values.png}
	}
	\caption{Using the $Z$ statistics from Figure \ref{fig:p_values}, highlighted in red are significant pixels at the $5\sigma$ significance level corrected for multiple tests using the Bonferroni correction.}
	\label{fig:critical_values}
\end{figure}

>>>>

A sample of $Z$ statistics, along with significant pixels, are shown in Figure \ref{fig:p_values}. The Bonferroni correction was used to correct for multiple testing. The $Z$ statistics within image varied scan to scan, suggesting images in the test set were not quite as similar to each other as hoped for. Common significant pixels were picked up by the statistic, especially on the left edge. Fortunately only a few significant pixels were picked up from the 3D printed sample, implying only a few false positives were detected.

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width = \textwidth]{../figures/meanVar/p_values.png}
		\caption{$\Phi(Z)$}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width = \textwidth]{../figures/meanVar/critical_values.png}
		\caption{Significant pixels}
	\end{subfigure}
	\caption{A sample of $Z$ statistics obtained from comparing a scan from the test set to the true image. In a) the $Z$ statistics were transformed using the standard Normal c.d.f. In b) highlighted in red are significant pixels at the $5\sigma$ significance level corrected for multiple tests using the Bonferroni correction.}
	\label{fig:p_values}
\end{figure*}
